Title here

### 2020-09-09 paper/paper.Rmd
figured out a way to display the animation using 16 frames - bad plot for now

dt %>% explore_proj_pca(facet = algo, size = 7, alpha = 0.5)
#dt %>% explore_proj_pca(facet = algo, axis = 2)

@@

@@

@@

>>>>

dt %>% explore_proj_pca(facet = algo, size = 7, alpha = 0.5)
#dt %>% explore_proj_pca(facet = algo, axis = 2)
```

@@

```{r animated-pca, fig.height = 8, fig.cap = "\\label{animated-pca} 16 frames from animated PCA plot ." }
rl <- lapply(list.files(here::here("figures/animated_pca/"),full.names = TRUE)[1:16], png::readPNG)
gl <-  lapply(rl, grid::rasterGrob)
gridExtra::grid.arrange(grobs=gl)
```

@@

1. how does the printed data object looks like?

Do I talk about the work done in the tourr package?

@@

2.
